MSF_Groupwork-NBA_shotlog

### 2016-10-10 MSFGroupwork-NBAHotHand.Rmd
Installing and calling is seperated

##Installing packages and calling libraries
```{r}
install.packages('reshape')
library(reshape)
library(ggplot2)

@@

```
### Home Advantage analysis
```{r}
# replacing W/L in column "W" with 1/0 (1 for win, 0 for loss)
df[,"W"] <- as.character(df[,"W"])

>>>>

## Installing libraries

```{r}
install.packages('reshape')

## Calling libraries
```{r}
library(reshape)
library(ggplot2)

@@

### Home Advantage analysis

```{r}
# replacing W/L in column "W" with 1/0 (1 for win, 0 for loss)
df[,"W"] <- as.character(df[,"W"])
